Lucid: Lifting-based Uncertain Control Invariant Dynamics

### 2025-07-28 docs/paper/figures/architecture.tex
feat: update paper

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners},
            output-block/.style={rectangle, draw, fill=green!20, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners},
            block/.style={rectangle, draw, fill=accent!20, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners},
            arrow/.style={thick,->,>=latex},
            % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[doc] (input) {Config\\(.yaml?)};

>>>>

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
            input-block/.style={rectangle, draw, fill=red!10!white, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            output-block/.style={rectangle, draw, fill=green!20!white, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            block/.style={rectangle, draw, fill=accent!20!white, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            arrow/.style={thick,->,>=latex},
            % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[doc] (input) {Configuration\\[.2em]\textit{.yaml/.json}};

### 2025-07-28 docs/paper/figures/steps.tex
feat: update paper

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=green!20, text width=2cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[input-block] (input) {Collect samples $\{(x^i,a^i, x_+^i)\}_{i=1}^N$};

        % Lucid blocks
        \node[block, right=of input] (estimator) {Fit the estimator $\hat{f}\colon \X\times\A \to \X$};
        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X\times\A \to \mathbb{R}^M$};
        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
        \node[block, below=of apply-lattice] (optimizer) {Solve the LP};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{\lucid}}] {};

        % Output block
        \node[output-block, left=of optimizer] (output) {Barrier certificate\\+\\Safety probability};

        % Arrows
        \draw[arrow] (input) -- (estimator);
        \draw[arrow] (estimator) -- (feature);
        \draw[arrow] (feature) -- (lattice);
        \draw[arrow] (lattice) -- (apply-lattice);
        \draw[arrow] (apply-lattice) -- (optimizer);
        \draw[arrow] (optimizer) -- (output);

>>>>

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
            input-block/.style={rectangle, draw, fill=white, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            output-block/.style={rectangle, draw, fill=green!20, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            block/.style={rectangle, draw, fill=accent!20, text width=3.7cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=green!20, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            inv/.style={}, 
            arrow/.style={thick,->,>=latex}
        ]

        % Input block
        \node[input-block] (samples) {Collect samples $\{(x^i,a^i, x_+^i)\}_{i=1}^N$};

        % Lucid blocks
        \node[block, right=of samples] (estimator) {Fit the estimator 
        $\E[f(X_+)\!\mid\! X=x,A=a]$
        % $\hat{f}\colon \X\times\A \to \X$
        };
        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X \to \mathbb{R}^{2M+1}$};
        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
        \node[block, below=of apply-lattice] (optimizer) {Solve the LP};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{\lucid}}] {};

        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_u$};

        % Output block
        \node[output-block, left=of optimizer, yshift=.75cm] (output) {Barrier certificate};
        \node[output-block, left=of optimizer, yshift=-.75cm] (output2) {Safety probability};

        % Arrows
        \draw[arrow] (samples) -- (estimator);
        \draw[arrow] (specification) -- (lattice);
        \draw[arrow] (estimator) -- (feature);
        \draw[arrow] (feature) -- (lattice);
        \draw[arrow] (lattice) -- (apply-lattice);
        \draw[arrow] (apply-lattice) -- (optimizer);
        \draw[arrow] (optimizer.170) -- (output.east);
        \draw[arrow] (optimizer.190) -- (output2.east);
